---
title: "Pareto design search for the CRD example, MSE(LP) criteria"
output: html_notebook
---


```{r}
library(data.table)
rm(list = ls())
```

Functions: criteria and search functions
```{r}
source("functions/label.R")
source("functions/transform.R")
source("functions/candidate_set_full.R")

source("functions/pareto_criteria_trace.R")
source("functions/pareto_search_functions_trace.R")
```

Specify parameters of the experiment

```{r}
K = 5
Levels = list(1:3,1:3,1:3,1:3,1:3) 

cand.full.extended = candidate_set_full(cand.trt = candidate_trt_set(Levels, K), K)

#cand.full.extended[,1:22]
#cand.full.extended[,23:52]

P = 21
Q = 30
Nruns = 40   
```

Specify the parameters of the search
```{r}
Nstarts = 1500
Biter = 500

alpha.LP = 1 - 0.95^(1./(P-1))
alpha.LoFL = 1 - 0.95^(1./Q)

W = matrix(1, nrow=1, ncol = P-1)
W[6:10] = 1./4
W = matrix(W/sum(W), nrow=1)

## Primary terms - full quadratic model, potential - QxL and LxLxL terms
cand.full = as.matrix(cand.full.extended[,1:(P+Q+1)])

tau2 = 1.0;       # tau2 = 1./Q
tau = sqrt(tau2)


## The best values of the three criteria -- obtained by single-objective optimization

crit.optim.1 <- c(0.695740449865902, 12.4662541755692, 0.276922940150295)  # tau2 = 1
crit.optim.Q <- c(0.695740449865902, 0.441104911412888, 0.0883278761177315)  # tau2 = 1/Q

crit.optim = crit.optim.1   # change to crit.optim.Q for tau2 = 1/q

seeds = 726491    # seeds = 163105

save.image("output/CRD_setup_L.RData")

```

```{r}
## There is a function that performs the search as below
# PF1 = Search.pareto.L(cand.full)
```

Search -- but in the global environment

```{r}

cand.full = as.matrix(cand.full)
set.seed(seeds)
  list.nd = list()
   beta_q = matrix(rnorm(Biter*Q, mean=0, sd=tau),  
                  ncol = Biter)    # to be amended if not iid
  
  start_time = Sys.time()
  for (k in 1:Nstarts)
  {
    paste("Current iteration:", k, sep = " ")
    initial = initial.full(cand.full)
    Labels = initial$Labels
    Xp = initial$Xp; Xq = initial$Xq
    if (k==1) 
    {
      pareto.opt = pareto_criteria_trace(Labels, Xp, Xq, beta_q)
      # initiate the set of non-dominant designs and criteria values
      list.nd = update.nd_list(list.nd, Labels = Labels, p.crit = pareto.opt)$l
    }
    s = 1
    while (s==1)
    {
      Xs = pareto.swap.full.L(Labels, Xp, Xq, cand.full, list.nd)
      Labels = Xs$Labels; Xp = Xs$Xp; Xq = Xs$Xq;
      list.nd = Xs$list.nd
      s = Xs$search
      paste("Number of designs =", length(list.nd), sep = " ")
    }
  }
  finish_time = Sys.time()
  time = finish_time - start_time
  
  list.designs = list()
  for (l in 1:length(list.nd)){
    list.designs = append(list.designs, list(append(list.nd[[l]], 
                                                    list(X.full = cand.full[list.nd[[l]]$labels,]))))
  }
```


```{r}
save.image("output/CRD_L_result.RData")
```

```{r}
load("output/CRD_L_result.RData")
```

Look at the criteria values of the designs -- store them in the dt_coords dataset

```{r}
dt_coords = data.frame(matrix(0, ncol = 4, nrow = length(list.designs)), 
                       row.names = 1:length(list.designs)); colnames(dt_coords) = c("LP", "LoF", "MSE", "df")

for (l in 1:length(list.designs)) {
  dt_coords[l,] = c(list.designs[[l]]$p.crit$values$LP, 
                    list.designs[[l]]$p.crit$values$LoF_LP, 
                    list.designs[[l]]$p.crit$values$mse,
                    Nruns - nlevels(as.factor(list.nd[[l]]$labels)))
}
dt_coords

dt_coords$label <- 1:nrow(dt_coords)
dt_coords[order(dt_coords$LP),]
dt_coords[order(dt_coords$LoF),]
dt_coords[order(dt_coords$MSE),]

```

Designs' efficiency values with respect to individual criteria

```{r}
nc <- ncol(dt_coords)
dt_coords[, nc+(1:3)] <- t(apply(dt_coords[,1:3], 1, function(x) crit.optim/x))
names(dt_coords)[nc+(1:3)] <- c("LP", "LoF(LP)", "MSE(L)")
dt_coords

```

Choose some designs -- using the weights

```{r}
m.kappa <- matrix(c(0.5, 0.5, 0,
                   0.5, 0, 0.5,
                   0, 0.5, 0.5,
                   rep(1./3, 3),
                   0.5, 0.25, 0.25,
                   0.25, 0.5, 0.25,
                   0.25, 0.25, 0.5,
                   2./3, 0.0, 1./3,
                   2./3, 1./3, 0.0, 
                   1./3, 0.0, 2./3,
                   1./3, 2./3, 0.0),
                 ncol = 3, byrow = TRUE)
```

dt_w contains compound criteria values of the designs, with the weights from m.kappa:

```{r}
ncoords = ncol(dt_coords)
dt_w = dt_coords

for (k in 1:(nrow(m.kappa))) {   
  
  dt_w[,ncoords + k] <- apply(as.matrix(dt_w[, ncoords - (2:0)]), 1, function(x) prod(x^m.kappa[k,]))
  colnames(dt_w)[ncoords + k] <- paste0("weighted_",k)

  }

print(dt_w)

```



Output: each .csv contains a table with designs (design labels) and their component criteria efficiency values, ordered by their performance w.r.t. to the weights allocation. 
In total -- 11 output files for each value of $\tau^2$.



```{r}
for (k in 1:(nrow(m.kappa))) {
  
  print(dt_w[order(-dt_w[, ncoords+k]),])
  write.csv(data.table(dt_w[order(-dt_w[, ncoords+k]),]),
            paste0("output/tables/MSEL_designs_weighted_", k, ".csv"))
  
}
```